---
title: "Turo.com TX Group Project"
author: "Hua Yang"
date: "2022-11-24"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(dplyr)
library(e1071)
library(knitr)
library(readr)
knitr::opts_chunk$set(echo = TRUE)
```

## GBA 5140 Statistics Essentials for Business Analytics
## Turo Project Description
## team captain: Hua Yang
## team member: liwu Dong, Yi Wei, Yiwen Huang

Purpose
This project provides hands-on experience of working with real-world data collected from a popular peer-to-peer online car sharing platform. Using statistics knowledge and R programming skills you learned from this course, you will explore and clean the dataset, build multiple linear regression models, interpret the results, discuss business insights, and document the whole process and your conclusion in the form of a report.
Data
This dataset was collected from a popular car sharing website Turo.com. See examples of website at the end of this document.
Read dataset “turo.data.5140” into RStudio using “readRDS” function (note it is not in csv format).
The following table includes descriptions of all variables in the dataset.

Instructions

Please construct a single R script file, which includes all your programs achieving the following tasks, in the corresponding order. Make sure your R script can be executed without any warning or error.


```{r }

```

**1.Load the data into RStudio.(contribute:Hua Yang)**

```{r }
setwd('/Users/xiaoqin/Documents/Business Analytics/5140/groupProject')
turo_df<-readRDS('turo.data.5140')
```

**2.Extract all the observations from the state your group is assigned to, and use this subset for the following tasks.(contribute:Hua Yang)**

```{r}
turo_tx <- turo_df %>%
  filter(car.state=="tx")
```

**3.Compute summary statistics (exclude missing values by setting na.rm = TRUE) and generate charts for ALL variables in the dataset. For each continuous variable, compute min, first quartile, medium, third quartile, max, mean, standard deviation, and skewness as summary statistics, and draw histogram. For each categorical variable, compute frequency and relative frequency distributions, and draw bar chart.(contribute:Hua Yang)**
```{r}
#load to csv
turo_tx <- read_csv('turoTX.csv')
print("There have 22 continuouse var and 30 categorical var(8 char,2 num and 21 logi")

#summarise each var and draw hist to continuouse var, bar to categorical var
#1.continuouse var:car.deliver.airport.num
car.deliver.airport.num.summary <- turo_tx %>% 
  summarise_at(vars(car.deliver.airport.num),
               list(min=min, Q1=~quantile(., probs = 0.25),
                    medium=median, Q3=~quantile(., probs = 0.75),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.deliver.airport.num.summary
#car.deliver.airport.num Histofram")
hist(turo_tx$car.deliver.airport.num,xlab="car.deliver.airport.num",main="Histogram of car.deliver.airport.num")

#2.continuouse var:car.deliver.hotel.num
car.deliver.hotel.num.summary <- turo_tx %>% 
  summarise_at(vars(car.deliver.hotel.num),
               list(min=min, Q1=~quantile(., probs = 0.25),
                    medium=median, Q3=~quantile(., probs = 0.75),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.deliver.hotel.num.summary
#car.deliver.hotel.num Histofram")
hist(turo_tx$car.deliver.hotel.num,xlab="car.deliver.hotel.num",main="Histogram of car.deliver.hotel.num")


#3.continuouse var:car.deliver.to.you.num
car.deliver.to.you.num.summary <- turo_tx %>% 
  summarise_at(vars(car.deliver.to.you.num),
               list(min=min, Q1=~quantile(., probs = 0.25),
                    medium=median, Q3=~quantile(., probs = 0.75),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.deliver.to.you.num.summary
#car.deliver.to.you.num Histofram")
hist(turo_tx$car.deliver.to.you.num,xlab="car.deliver.to.you.num",main="Histogram of car.deliver.to.you.num")


#4.continuouse var:car.deliver.train.station.num
car.deliver.train.station.num.summary <- turo_tx %>% 
  summarise_at(vars(car.deliver.train.station.num),
               list(min=min, Q1=~quantile(., probs = 0.25),
                    medium=median, Q3=~quantile(., probs = 0.75),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.deliver.train.station.num.summary
#car.deliver.train.station.num Histofram")
hist(turo_tx$car.deliver.train.station.num,xlab="car.deliver.train.station.num",main="Histogram of car.deliver.train.station.num")


#5.continuouse var:car.displayed.turo.review.num
car.displayed.turo.review.num.summary <- turo_tx %>% 
  summarise_at(vars(car.displayed.turo.review.num),
               list(min=min, Q1=~quantile(., probs = 0.25),
                    medium=median, Q3=~quantile(., probs = 0.75),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.displayed.turo.review.num.summary
#car.displayed.turo.review.num Histofram")
hist(turo_tx$car.displayed.turo.review.num,xlab="car.displayed.turo.review.num",main="Histogram of car.displayed.turo.review.num")

#6.continuouse var:car.displayed.turo.review.num.past.12m
car.displayed.turo.review.num.past.12m.summary <- turo_tx %>% 
  summarise_at(vars(car.displayed.turo.review.num.past.12m),
               list(min=min, Q1=~quantile(., probs = 0.25),
                    medium=median, Q3=~quantile(., probs = 0.75),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.displayed.turo.review.num.past.12m.summary
#car.displayed.turo.review.num.past.12m Histofram")
hist(turo_tx$car.displayed.turo.review.num.past.12m,xlab="car.displayed.turo.review.num.past.12m",main="Histogram of car.displayed.turo.review.num.past.12m")

#7.continuouse var:car.displayed.turo.review.num.past.18m
car.displayed.turo.review.num.past.18m.summary <- turo_tx %>% 
  summarise_at(vars(car.displayed.turo.review.num.past.18m),
               list(min=min, Q1=~quantile(., probs = 0.25),
                    medium=median, Q3=~quantile(., probs = 0.75),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.displayed.turo.review.num.past.18m.summary
#car.displayed.turo.review.num.past.18m Histofram")
hist(turo_tx$car.displayed.turo.review.num.past.18m,xlab="car.displayed.turo.review.num.past.18m",main="Histogram of car.displayed.turo.review.num.past.18m")

#8.continuouse var:car.displayed.turo.review.num.past.6m
car.displayed.turo.review.num.past.6m.summary <- turo_tx %>% 
  summarise_at(vars(car.displayed.turo.review.num.past.6m),
               list(min=min, Q1=~quantile(., probs = 0.25),
                    medium=median, Q3=~quantile(., probs = 0.75),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.displayed.turo.review.num.past.6m.summary
#car.displayed.turo.review.num.past.6m Histofram")
hist(turo_tx$car.displayed.turo.review.num.past.6m,xlab="car.displayed.turo.review.num.past.6m",main="Histogram of car.displayed.turo.review.num.past.6m")

#9.continuouse var:car.displayed.user.review.num
car.displayed.user.review.num.summary <- turo_tx %>% 
  summarise_at(vars(car.displayed.user.review.num),
               list(min=min, Q1=~quantile(., probs = 0.25),
                    medium=median, Q3=~quantile(., probs = 0.75),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.displayed.user.review.num.summary
#car.displayed.user.review.num Histofram")
hist(turo_tx$car.displayed.user.review.num,xlab="car.displayed.user.review.num",main="Histogram of car.displayed.user.review.num")

#10.continuouse var:car.displayed.user.review.num.past.12m
car.displayed.user.review.num.past.12m.summary <- turo_tx %>% 
  summarise_at(vars(car.displayed.user.review.num.past.12m),
               list(min=min, Q1=~quantile(., probs = 0.25),
                    medium=median, Q3=~quantile(., probs = 0.75),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.displayed.user.review.num.past.12m.summary
#car.displayed.user.review.num.past.12m Histofram")
hist(turo_tx$car.displayed.user.review.num.past.12m,xlab="car.displayed.user.review.num.past.12m",main="Histogram of car.displayed.user.review.num.past.12m")

#11.continuouse var:car.displayed.turo.review.num.past.18m
car.displayed.turo.review.num.past.18m.summary <- turo_tx %>% 
  summarise_at(vars(car.displayed.turo.review.num.past.18m),
               list(min=min, Q1=~quantile(., probs = 0.25),
                    medium=median, Q3=~quantile(., probs = 0.75),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.displayed.turo.review.num.past.18m.summary
#car.displayed.turo.review.num.past.18m Histofram")
hist(turo_tx$car.displayed.turo.review.num.past.18m,xlab="car.displayed.turo.review.num.past.18m",main="Histogram of car.displayed.turo.review.num.past.18m")

#12.continuouse var:car.displayed.user.review.num.past.6m
car.displayed.user.review.num.past.6m.summary <- turo_tx %>% 
  summarise_at(vars(car.displayed.user.review.num.past.6m),
               list(min=min, Q1=~quantile(., probs = 0.25),
                    medium=median, Q3=~quantile(., probs = 0.75),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.displayed.user.review.num.past.6m.summary
#car.displayed.user.review.num.past.6m Histofram")
hist(turo_tx$car.displayed.user.review.num.past.6m,xlab="car.displayed.user.review.num.past.6m",main="Histogram of car.displayed.user.review.num.past.6m")

#13.continuouse var:car.extra.num
car.extra.num.summary <- turo_tx %>% 
  summarise_at(vars(car.extra.num),
               list(min=min, Q1=~quantile(., probs = 0.25),
                    medium=median, Q3=~quantile(., probs = 0.75),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.extra.num.summary
#car.extra.num Histofram")
hist(turo_tx$car.extra.num,xlab="car.extra.num",main="Histogram of car.extra.num")

#14.continuouse var:car.faq.num
car.faq.num.summary <- turo_tx %>% 
  summarise_at(vars(car.faq.num),
               list(min=min, Q1=~quantile(., probs = 0.25),
                    medium=median, Q3=~quantile(., probs = 0.75),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.faq.num.summary
#car.faq.num Histofram")
hist(turo_tx$car.faq.num,xlab="car.faq.num",main="Histogram of car.faq.num")

#15.continuouse var:car.miles.included
car.miles.included.summary <- turo_tx %>% 
  summarise_at(vars(car.miles.included),
               list(min=min, Q1=~quantile(., probs = 0.25,na.rm = TRUE),
                    medium=median, Q3=~quantile(., probs = 0.75,na.rm = TRUE),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.miles.included.summary
#car.miles.included Histofram")
hist(turo_tx$car.miles.included,xlab="car.miles.included",main="Histogram of car.miles.included")

#16.continuouse var:car.photo.num
car.photo.num.summary <- turo_tx %>% 
  summarise_at(vars(car.photo.num),
               list(min=min, Q1=~quantile(., probs = 0.25,na.rm = TRUE),
                    medium=median, Q3=~quantile(., probs = 0.75,na.rm = TRUE),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.photo.num.summary
#car.photo.num Histofram")
hist(turo_tx$car.photo.num,xlab="car.photo.num",main="Histogram of car.photo.num")

#17.continuouse var:car.self.pickup.avg.price
car.self.pickup.avg.price.summary <- turo_tx %>% 
  summarise_at(vars(car.self.pickup.avg.price),
               list(min=min, Q1=~quantile(., probs = 0.25,na.rm = TRUE),
                    medium=median, Q3=~quantile(., probs = 0.75,na.rm = TRUE),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.self.pickup.avg.price.summary
#car.self.pickup.avg.price Histofram")
hist(turo_tx$car.self.pickup.avg.price,xlab="car.self.pickup.avg.price",main="Histogram of car.self.pickup.avg.price")

#18.continuouse var:car.extra.mile.fee
car.extra.mile.fee.summary <- turo_tx %>% 
  summarise_at(vars(car.extra.mile.fee),
               list(min=min, Q1=~quantile(., probs = 0.25,na.rm = TRUE),
                    medium=median, Q3=~quantile(., probs = 0.75,na.rm = TRUE),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.extra.mile.fee.summary
#car.extra.mile.fee Histofram")
hist(turo_tx$car.extra.mile.fee,xlab="car.extra.mile.fee",main="Histogram of car.extra.mile.fee")

#19.continuouse var:car.self.pickup.num
car.self.pickup.num.summary <- turo_tx %>% 
  summarise_at(vars(car.self.pickup.num),
               list(min=min, Q1=~quantile(., probs = 0.25),
                    medium=median, Q3=~quantile(., probs = 0.75),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.self.pickup.num.summary
#car.self.pickup.num Histofram")
hist(turo_tx$car.self.pickup.num,xlab="car.self.pickup.num",main="Histogram of car.self.pickup.num")

#20.continuouse var:car.trip.price
car.trip.price.summary <- turo_tx %>% 
  summarise_at(vars(car.trip.price),
               list(min=min, Q1=~quantile(., probs = 0.25,na.rm = TRUE),
                    medium=median, Q3=~quantile(., probs = 0.75,na.rm = TRUE),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
car.trip.price.summary
#car.trip.price Histofram")
hist(turo_tx$car.trip.price,xlab="car.trip.price",main="Histogram of car.trip.price")

#21.continuouse var:host.car.num
host.car.num.summary <- turo_tx %>% 
  summarise_at(vars(host.car.num),
               list(min=min, Q1=~quantile(., probs = 0.25),
                    medium=median, Q3=~quantile(., probs = 0.75),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
host.car.num.summary
#host.car.num Histofram")
hist(turo_tx$host.car.num,xlab="host.car.num",main="Histogram of host.car.num")

#22.continuouse var:host.tenure.in.weeks
host.tenure.in.weeks.summary <- turo_tx %>% 
  summarise_at(vars(host.tenure.in.weeks),
               list(min=min, Q1=~quantile(., probs = 0.25,na.rm = TRUE),
                    medium=median, Q3=~quantile(., probs = 0.75,na.rm = TRUE),
                    max=max,mean=mean,sd=sd,ske=skewness),na.rm = TRUE)
host.tenure.in.weeks.summary
#host.tenure.in.weeks Histofram")
hist(turo_tx$host.tenure.in.weeks,xlab="host.tenure.in.weeks",main="Histogram of host.tenure.in.weeks")

#23.categorical var:car.doors
car.doors.freq <- turo_tx %>%
  group_by(car.doors)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.doors.freq)
#car.doors bar chart
barplot(car.doors.freq$n,names.arg=car.doors.freq$car.doors,
        xlab="car.doors",ylab="Frequency",main="Bar Chart of car.doors")

#24.categorical var:car.extra.beach.gear
car.extra.beach.gear.freq <- turo_tx %>%
  group_by(car.extra.beach.gear)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.extra.beach.gear.freq)
#car.extra.beach.gear bar chart
barplot(car.extra.beach.gear.freq$n,names.arg=car.extra.beach.gear.freq$car.extra.beach.gear,
        xlab="car.extra.beach.gear",ylab="Frequency",main="Bar Chart of car.extra.beach.gear")

#25.categorical var:car.extra.child.safety.seat
car.extra.child.safety.seat.freq <- turo_tx %>%
  group_by(car.extra.child.safety.seat)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.extra.child.safety.seat.freq)
#car.extra.child.safety.seat bar chart
barplot(car.extra.child.safety.seat.freq$n,names.arg=car.extra.child.safety.seat.freq$car.extra.child.safety.seat,
        xlab="car.extra.child.safety.seat",ylab="Frequency",main="Bar Chart of car.extra.child.safety.seat")

#26.categorical var:car.extra.cooler
car.extra.cooler.freq <- turo_tx %>%
  group_by(car.extra.cooler)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.extra.cooler.freq)
#car.extra.cooler bar chart
barplot(car.extra.cooler.freq$n,names.arg=car.extra.cooler.freq$car.extra.cooler,
        xlab="car.extra.cooler",ylab="Frequency",main="Bar Chart of car.extra.cooler")

#27.categorical var:car.extra.one.way.trip
car.extra.one.way.trip.freq <- turo_tx %>%
  group_by(car.extra.one.way.trip)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.extra.one.way.trip.freq)
#car.extra.one.way.trip bar chart
barplot(car.extra.one.way.trip.freq$n,names.arg=car.extra.one.way.trip.freq$car.extra.one.way.trip,
        xlab="car.extra.one.way.trip",ylab="Frequency",main="Bar Chart of car.extra.one.way.trip")

#28.categorical var:car.extra.pet.fee
car.extra.pet.fee.freq <- turo_tx %>%
  group_by(car.extra.pet.fee)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.extra.pet.fee.freq)
#car.extra.pet.fee bar chart
barplot(car.extra.pet.fee.freq$n,names.arg=car.extra.pet.fee.freq$car.extra.pet.fee,
        xlab="car.extra.pet.fee",ylab="Frequency",main="Bar Chart of car.extra.pet.fee")

#29.categorical var:car.extra.phone.mount
car.extra.phone.mount.freq <- turo_tx %>%
  group_by(car.extra.phone.mount)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.extra.phone.mount.freq)
#car.extra.phone.mount bar chart
barplot(car.extra.phone.mount.freq$n,names.arg=car.extra.phone.mount.freq$car.extra.phone.mount,
        xlab="car.extra.phone.mount",ylab="Frequency",main="Bar Chart of car.extra.phone.mount")

#30.categorical var:car.extra.portable.gps
car.extra.portable.gps.freq <- turo_tx %>%
  group_by(car.extra.portable.gps)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.extra.portable.gps.freq)
#car.extra.portable.gps bar chart
barplot(car.extra.portable.gps.freq$n,names.arg=car.extra.portable.gps.freq$car.extra.portable.gps,
        xlab="car.extra.portable.gps",ylab="Frequency",main="Bar Chart of car.extra.portable.gps")

#31.categorical var:car.extra.post.trip.cleaning
car.extra.post.trip.cleaning.freq <- turo_tx %>%
  group_by(car.extra.post.trip.cleaning)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.extra.post.trip.cleaning.freq)
#car.extra.post.trip.cleaning bar chart
barplot(car.extra.post.trip.cleaning.freq$n,names.arg=car.extra.post.trip.cleaning.freq$car.extra.post.trip.cleaning,
        xlab="car.extra.post.trip.cleaning",ylab="Frequency",main="Bar Chart of car.extra.post.trip.cleaning")

#32.categorical var:car.extra.prepaid.ev.recharge
car.extra.prepaid.ev.recharge.freq <- turo_tx %>%
  group_by(car.extra.prepaid.ev.recharge)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.extra.prepaid.ev.recharge.freq)
#car.extra.prepaid.ev.recharge bar chart
barplot(car.extra.prepaid.ev.recharge.freq$n,names.arg=car.extra.prepaid.ev.recharge.freq$car.extra.prepaid.ev.recharge,
        xlab="car.extra.prepaid.ev.recharge",ylab="Frequency",main="Bar Chart of car.extra.prepaid.ev.recharge")

#33.categorical var:car.extra.prepaid.refuel
car.extra.prepaid.refuel.freq <- turo_tx %>%
  group_by(car.extra.prepaid.refuel)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.extra.prepaid.refuel.freq)
#car.extra.prepaid.refuel bar chart
barplot(car.extra.prepaid.refuel.freq$n,names.arg=car.extra.prepaid.refuel.freq$car.extra.prepaid.refuel,
        xlab="car.extra.prepaid.refuel",ylab="Frequency",main="Bar Chart of car.extra.prepaid.refuel")

#34.categorical var:car.extra.stroller
car.extra.stroller.freq <- turo_tx %>%
  group_by(car.extra.stroller)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.extra.stroller.freq)
#car.extra.stroller bar chart
barplot(car.extra.stroller.freq$n,names.arg=car.extra.stroller.freq$car.extra.stroller,
        xlab="car.extra.stroller",ylab="Frequency",main="Bar Chart of car.extra.stroller")

#35.categorical var:car.extra.unlimited.mileage
car.extra.unlimited.mileage.freq <- turo_tx %>%
  group_by(car.extra.unlimited.mileage)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.extra.unlimited.mileage.freq)
#car.extra.unlimited.mileage bar chart
barplot(car.extra.unlimited.mileage.freq$n,names.arg=car.extra.unlimited.mileage.freq$car.extra.unlimited.mileage,
        xlab="car.extra.unlimited.mileage",ylab="Frequency",main="Bar Chart of car.extra.unlimited.mileage")

#36.categorical var:car.instant.booke
car.instant.book.freq <- turo_tx %>%
  group_by(car.instant.book)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.instant.book.freq)
#car.instant.book bar chart
barplot(car.instant.book.freq$n,names.arg=car.instant.book.freq$car.instant.book,
        xlab="car.instant.book",ylab="Frequency",main="Bar Chart of car.instant.book")

#37.categorical var:car.insurance
car.insurance.freq <- turo_tx %>%
  group_by(car.insurance)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.insurance.freq)
#car.insurance bar chart
barplot(car.insurance.freq$n,names.arg=car.insurance.freq$car.insurance,
        xlab="car.insurance",ylab="Frequency",main="Bar Chart of car.insurance")

#38.categorical var:car.make
car.make.freq <- turo_tx %>%
  group_by(car.make)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.make.freq)
#car.make bar chart
barplot(car.make.freq$n,names.arg=car.make.freq$car.make,
        xlab="car.make",ylab="Frequency",main="Bar Chart of car.make")

#39.categorical var:car.model
car.model.freq <- turo_tx %>%
  group_by(car.model)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.model.freq)
#car.model bar chart
barplot(car.model.freq$n,names.arg=car.model.freq$car.model,
        xlab="car.model",ylab="Frequency",main="Bar Chart of car.model")

#40.categorical var:car.photo.verified
car.photo.verified.freq <- turo_tx %>%
  group_by(car.photo.verified)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.photo.verified.freq)
#car.photo.verified bar chart
barplot(car.photo.verified.freq$n,names.arg=car.photo.verified.freq$car.photo.verified,
        xlab="car.photo.verified",ylab="Frequency",main="Bar Chart of car.photo.verified")

#41.categorical var:car.power
car.power.freq <- turo_tx %>%
  group_by(car.power)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.power.freq)
#car.power bar chart
barplot(car.power.freq$n,names.arg=car.power.freq$car.power,
        xlab="car.power",ylab="Frequency",main="Bar Chart of car.power")

#42.categorical var:car.rental.type
car.rental.type.freq <- turo_tx %>%
  group_by(car.rental.type)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.rental.type.freq)
#car.rental.type bar chart
barplot(car.rental.type.freq$n,names.arg=car.rental.type.freq$car.rental.type,
        xlab="car.rental.type",ylab="Frequency",main="Bar Chart of car.rental.type")

#43.categorical var:car.state
car.state.freq <- turo_tx %>%
  group_by(car.state)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.state.freq)
#car.state bar chart
barplot(car.state.freq$n,names.arg=car.state.freq$car.state,
        xlab="car.state",ylab="Frequency",main="Bar Chart of car.state")

#44.categorical var:car.transmission
car.transmission.freq <- turo_tx %>%
  group_by(car.transmission)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.transmission.freq)
#car.transmission bar chart
barplot(car.transmission.freq$n,names.arg=car.transmission.freq$car.transmission,
        xlab="car.transmission",ylab="Frequency",main="Bar Chart of car.transmission")

#45.categorical var:car.turo.go
car.turo.go.freq <- turo_tx %>%
  group_by(car.turo.go)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.turo.go.freq)
#car.turo.go bar chart
barplot(car.turo.go.freq$n,names.arg=car.turo.go.freq$car.turo.go,
        xlab="car.turo.go",ylab="Frequency",main="Bar Chart of car.turo.go")

#46.categorical var:car.year
car.year.freq <- turo_tx %>%
  group_by(car.year)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.year.freq)
#car.year bar chart
barplot(car.year.freq$n,names.arg=car.year.freq$car.year,
        xlab="car.year",ylab="Frequency",main="Bar Chart of car.year")

#47.categorical var:host.all.star
host.all.star.freq <- turo_tx %>%
  group_by(host.all.star)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(host.all.star.freq)
#host.all.star bar chart
barplot(host.all.star.freq$n,names.arg=host.all.star.freq$host.all.star,
        xlab="host.all.star",ylab="Frequency",main="Bar Chart of host.all.star")

#48.categorical var:host.location.available
host.location.available.freq <- turo_tx %>%
  group_by(host.location.available)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(host.location.available.freq)
#host.location.available bar chart
barplot(host.location.available.freq$n,names.arg=host.location.available.freq$host.location.available,
        xlab="host.location.available",ylab="Frequency",main="Bar Chart of host.location.available")

#49.categorical var:host.verified.approved.to.drive
host.verified.approved.to.drive.freq <- turo_tx %>%
  group_by(host.verified.approved.to.drive)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(host.verified.approved.to.drive.freq)
#host.verified.approved.to.drive bar chart
barplot(host.verified.approved.to.drive.freq$n,names.arg=host.verified.approved.to.drive.freq$host.verified.approved.to.drive,
        xlab="host.verified.approved.to.drive",ylab="Frequency",main="Bar Chart of host.verified.approved.to.drive")

#50.categorical var:host.verified.email
host.verified.email.freq <- turo_tx %>%
  group_by(host.verified.email)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(host.verified.email.freq)
#host.verified.email bar chart
barplot(host.verified.email.freq$n,names.arg=host.verified.email.freq$host.verified.email,
        xlab="host.verified.email",ylab="Frequency",main="Bar Chart of host.verified.email")

#51.categorical var:host.verified.fb
host.verified.fb.freq <- turo_tx %>%
  group_by(host.verified.fb)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(host.verified.fb.freq)
#host.verified.fb bar chart
barplot(host.verified.fb.freq$n,names.arg=host.verified.fb.freq$host.verified.fb,
        xlab="host.verified.fb",ylab="Frequency",main="Bar Chart of host.verified.fb")


#52.categorical var:host.verified.phone
host.verified.phone.freq <- turo_tx %>%
  group_by(host.verified.phone)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(host.verified.phone.freq)
#host.verified.phone bar chart
barplot(host.verified.phone.freq$n,names.arg=host.verified.phone.freq$host.verified.phone,
        xlab="host.verified.phone",ylab="Frequency",main="Bar Chart of host.verified.phone")

#53.categorical var:car.city
car.city.freq <- turo_tx %>%
  group_by(car.city)%>%
  summarise(n=n())%>%
  mutate(relative_freq=n / sum(n))
head(car.city.freq)
#car.city bar chart
barplot(car.city.freq$n,names.arg=car.city.freq$car.city,
        xlab="car.city",ylab="Frequency",main="Bar Chart of car.city")

```

**4.Use Inter Quartile Range (IQR) method to identify outliers of all continuous variables, then remove all observations containing outliers.**
```{r}

```
**5.Remove all observations with missing values.**
```{r}

```
**6.Build a multiple linear regression model using car.trip.price as dependent variable. Select at least five independent variables. Treat each categorical variable as a single variable although it may be broken into multiple dummy variables. Try different models and choose the best one you can find.**

```{r}

```